---
title: "Soccer Players Data Visualization"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    social: menu
runtime: shiny
---

```{r load-packages, include=FALSE}
library(flexdashboard)
library(shiny)
library(tools)
library(tidyverse)
library(shinythemes)
library(rsconnect)
```

```{r load-data, include = FALSE}
players <- read_csv("data/players1.csv")
```


Sidebar {.sidebar}
=======================================================================

Click on the menus below to choose a combination variables to visualize. 

```{r choices}
theme <- shinytheme("cerulean")

selectInput(
  inputId = "y",
  label = "Y-axis:",
  choices = c(
    "Position" = "position",
    "Age" = "age",
    "Matches" = "matches",
    "Goals" = "goals",
    "Own Goals" = "own_goals",
    "Assists" = "assists",
    "Yellow Cards" = "yellow_cards",
    "Red Cards" = "red_cards",
    "Substituted On" = "substituted_on",
    "Substituted Off" = "substituted_off",
    "Market Value" = "market_value",
    "Age Range" = "age_range"
  ),
  selected = "position"
)

selectInput(
  inputId = "x",
  label = "X-axis:",
  choices = c(
    "Position" = "position",
    "Age" = "age",
    "Matches" = "matches",
    "Goals" = "goals",
    "Own Goals" = "own_goals",
    "Assists" = "assists",
    "Yellow Cards" = "yellow_cards",
    "Red Cards" = "red_cards",
    "Substituted On" = "substituted_on",
    "Substituted Off" = "substituted_off",
    "Market Value" = "market_value",
    "Age Range" = "age_range"
  ),
  selected = "market_value"
)

selectInput(
  inputId = "z",
  label = "Color by:",
  choices = c(
    "Position" = "position",
    "Age" = "age",
    "Matches" = "matches",
    "Goals" = "goals",
    "Own Goals" = "own_goals",
    "Assists" = "assists",
    "Yellow Cards" = "yellow_cards",
    "Red Cards" = "red_cards",
    "Substituted On" = "substituted_on",
    "Substituted Off" = "substituted_off",
    "Market Value" = "market_value",
    "Age Range" = "age_range"
  ),
  selected = "age"
)
```

Scatter vs. Jitter
=======================================================================

Row
-----------------------------------------------------------------------

### Scatterplot

```{r plot}

output$scatterplot <- renderPlot({
  ggplot(data = players, aes_string(
    x = input$x, y = input$y,
    color = input$z
  )) +
    geom_point() +
    labs(
      x = toTitleCase(str_replace_all(input$x, "_", " ")),
      y = toTitleCase(str_replace_all(input$y, "_", " ")),
      color = toTitleCase(str_replace_all(input$z, "_", " "))
    )
})

plotOutput(outputId = "scatterplot")
```

### Scatterplot with jitter

```{r plot_jitter}

output$scatterplotjitter <- renderPlot({
  ggplot(data = players, aes_string(
    x = input$x, y = input$y,
    color = input$z
  )) +
    geom_jitter() +
    labs(
      x = toTitleCase(str_replace_all(input$x, "_", " ")),
      y = toTitleCase(str_replace_all(input$y, "_", " ")),
      color = toTitleCase(str_replace_all(input$z, "_", " "))
    )
})

plotOutput(outputId = "scatterplotjitter")
```

Explanation 
=======================================================================

Jitter slightly shifts each data point in a scatter plot to reveal overlapping data points. This is especially useful when visualizing categorical data where many data points might be in the same place. 
